MLH1 Data Report

### 2019-12-27 doc/Main_Report_Results.rmd
re-starting effect quan measurements

## Variance in CO count

@@

I can show the variance boxplots?  Not sure if it's very helpful.
Use the same Datasets HQ and mol for the mean CO counts. Use both var and cV as dependant variables

DF.HetC.MixedModel.HQ.mol
DF.HetC.MixedModel.HQ

@@

@@

```{r DMC1.subsampling, echo=FALSE}

>>>>

# Variance in CO count

@@

@@

#make series for total dataset?
Var.Hist.total.mice <- ggplot(DF.HetC.MixedModel, aes(x = var, fill=sex)) + 
  geom_histogram(binwidth = 1, alpha=.6)  +
  ggtitle("Histograms of within mouse variance, all mice")
Var.Hist.total.mice <- Var.Hist.total.mice   + facet_wrap(~ strain, scales="free")
Var.Hist.total.mice

#DF.HetC.MixedModel.HQ
Var.Hist <- ggplot(DF.HetC.MixedModel.HQ, aes(x = var, fill=sex)) + 
  geom_histogram(binwidth = 1, alpha=.6)  + 
  ggtitle("Histograms of within mouse variance, 10 cell min")
Var.Hist <- Var.Hist   + facet_wrap(~ strain, scales="free")
Var.Hist

Var.Hist.15cells <- ggplot(DF.HetC.MixedModel.HQ[DF.HetC.MixedModel.HQ$Ncells >14,], aes(x = var, fill=sex)) + 
  geom_histogram(binwidth = 1, alpha=.6)  +   ggtitle("Histograms of within mouse variance, 15 cell min")
Var.Hist.15cells <- Var.Hist.15cells   + facet_wrap(~ strain, scales="free")
Var.Hist.15cells

A general pattern is that the female data has higher within mouse variance (both var and cV). I think the dissection date needs to be tested as a predictor factor.  It might be tricky to add the dissection date metric. 
Test if dissection date is more significant predictor than strain (for females)

(LEW females with top 3 variance are all from different dissection dates)

```{r cv.plots, echo=FALSE}

cV.Hist.total.mice <- ggplot(DF.HetC.MixedModel, aes(x =cV , fill=sex)) + 
  geom_histogram(binwidth = 1, alpha=.6)  +
  ggtitle("cV of within mouse variance, all mice")
cV.Hist.total.mice <- cV.Hist.total.mice   + facet_wrap(~ strain, scales="free")
cV.Hist.total.mice

#DF.HetC.MixedModel.HQ
cV.Hist <- ggplot(DF.HetC.MixedModel.HQ, aes(x = cV, fill=sex)) + 
  geom_histogram(binwidth = 1, alpha=.6)  + 
  ggtitle("cV of within mouse variance, 10 cell min")
cV.Hist <- cV.Hist   + facet_wrap(~ strain, scales="free")
cV.Hist

@@

```{r DMC1.subsampling, echo=FALSE, eval=FALSE}
